Implicit yaddayadda

### 2011-10-11 papers/PLDI2012/implicitization.tex
ajout d'une phrase qui explique ce qu'est A
refs to Z3 and Yices

The current working subset of paths, noted $P$, is stored using a
compact representation, such as binary decision diagrams.
We also maintain a set of active control points $A$, containing the points in $P_R$
that still need to be processed. 
We apply the Path-focused technique\cite{Monniaux_Gonnord_SAS11} to
the elements of $A$ until $A$ is empty. 
We also check which paths become feasible, so that we can include them into the
next subset of paths at the next iteration. These new feasible paths are
temporarily stored in a set $P'$. 
When $A$ is empty, it means the
invariant computation of the subgraph is finished. As proposed by
\citet{DBLP:conf/sas/GopanR07}, we can do some narrowing iterations.
These narrowing iterations allow to recover precision lost by
widening, before taking into account new feasible paths.
Thus, our technique combines both the advantages of \emph{Guided Static
Analysis} and \emph{Path-focusing}.
We then restart the analysis with a new subgraph if needed, by adding into $P$
the paths in $P'$. The set of active points $A$ is assigned to $A'$, which is
the set of control points that are starting points of a new feasible path in
$P'$.

@@

Guided static analysis from \citet{DBLP:conf/sas/GopanR07} yields at line 5 
$\lstinline|x_old| \in (-\infty,+\infty)$.
Path-focused technique from \citet{Monniaux_Gonnord_SAS11} performs slightly
better, and finds $\lstinline|x_old| \in (-\infty,10000)$.
Our combined technique gives us the expected invariant 
$\lstinline|x_old| \in (-10000,10000)$.

@@

\section{Conclusion}

>>>>

The current working subset of paths, noted $P$, is stored using a
compact representation, such as binary decision diagrams.
We also maintain a set of active control points $A$, containing the points in $P_R$
that still need to be processed. Each time the abstract value of a control point
$p$ is updated, $p$ is inserted in $A$.

We apply the Path-focused technique\cite{Monniaux_Gonnord_SAS11} to
the elements of $A$ until $A$ is empty. 
We also check which paths become feasible, so that we can include them into the
next subset of paths at the next iteration. These new feasible paths are
temporarily stored in a set $P'$. 
When $A$ is empty, it means the
invariant computation of the subgraph is finished. As proposed by
\citet{DBLP:conf/sas/GopanR07}, we can do some narrowing iterations.
These narrowing iterations allow to recover precision lost by
widening, before taking into account new feasible paths.
Thus, our technique combines both the advantages of \emph{Guided Static
Analysis} and \emph{Path-focusing}.
We then restart the analysis with a new subgraph if needed, by adding into $P$
the paths in $P'$. The set of active points $A$ is assigned to $A'$, which is
the set of control points that are starting points of a new feasible path in
$P'$.

@@

Guided static analysis from \citet{DBLP:conf/sas/GopanR07} yields at line 5
$\lstinline|x_old| \in~]-\infty,+\infty[$.
Path-focused technique from \citet{Monniaux_Gonnord_SAS11} performs slightly
better, and finds $\lstinline|x_old| \in~]-\infty,10000]$.
Our combined technique gives us the expected invariant 
$\lstinline|x_old| \in~[-10000,10000]$.

In this example, we see that our technique actually combines best of
\emph{Guided Static Analysis} and \emph{Path Focusing}. Still, we need to unroll
the loop once in order to get precise results. Section \ref{sec:disjunctive}
proposes a new technique that gives precise invariants without needing such
graph transformations.

@@

Our analyzer uses Yices \cite{DBLP:conf/cav/DutertreM06}
 or Microsoft Z3\cite{DBLP:conf/tacas/MouraB08} as SMT-solver.
\section{Conclusion}
